Volume reviews functions

### 2021-08-25 R/Volume reviews functions.Rmd
loggingsummary and loggingsimulation functions

# timberharvestedvolume
INPUT : inventory + fuel
OUTPUT : LoggedVolume

Si type != "RIL3fuelhollow"  ou (type == "manual"& fuel !="2"): 
LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"

Si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
LoggedVolume = ∑NoHollowLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".

@@

  LoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
}

@@

  NoHollowLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
  LoggedVolume <- sum(NoHollowLoggedVolume +
                        1-(otherloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
}

@@

INPUT : inventory + LoggedVolume/NoHollowLoggedVolume
OUTPUT : FuelVolume

si type = "RIL3fuel" ou (type == "manual"& fuel =="1"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*LoggedVolume

si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowLoggedVolume

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + otherloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
                    otherloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + otherloggingparameters$Purge*NoHollowLoggedVolume)
# damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees

>>>>

# timberharvestedvolume
INPUT : inventory + fuel
OUTPUT : TimberLoggedVolume

Si scenario != "RIL3fuelhollow"  ou (scenario == "manual"& fuel !="2"): 
TimberLoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"

Si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"): NoHollowTimberLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
TimberLoggedVolume = ∑NoHollowTimberLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".

@@

  TimberLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
}

@@

  NoHollowTimberLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
  TimberLoggedVolume <- sum(NoHollowTimberLoggedVolume +
                        1-(advancedloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
}

@@

INPUT : inventory + TimberLoggedVolume/NoHollowTimberLoggedVolume
OUTPUT : FuelVolume

si scenario = "RIL3fuel" ou (scenario == "manual"& fuel =="1"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*TimberLoggedVolume

si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowTimberLoggedVolume

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + advancedloggingparameters$Purge*TimberLoggedVolume) # Damage and purge (0.14)

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
                    advancedloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + advancedloggingparameters$Purge*NoHollowTimberLoggedVolume)
# damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees
